Analysis of the included studies

### 2023-05-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
commented out the chunk to check if knitting is interactive as it's not working

```{r}
#' if sourced, re-run the data cleaning step, in case something has changed 
#' else if through the terminal, use the arguments passed through the
#' commandline/make
if (is_null(getOption('knitr.in.progress'))) {
source(here::here('./scripts/orv_models_review_data_cleaning.R'))
args <- c(
  here::here("data", "review_data_long_cleaned.rds"),
  here::here("data", "review_data_compact_cleaned.rds"),
  here::here("data", "compact_data_with_citation_keys_cleaned.rds")
  )
} else {
 args <- commandArgs(trailingOnly = TRUE)
}
```

```{r}
# Create a folder for storing the figures

>>>>

```{r}
# if the figs folder doesn't exist, create it for storing the figures
figs_dir <- "figs"
